Verifying Demonstrations

### 2018-08-21 paper/adversary-model.tex
Adds tikz figures for system model, adds base witness adversary

This definition is illustrated in \cref{fig:system-model}.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{system-model.png}
  \caption{\label{fig:system-model}%
    An overview of the system model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
    and the time it happened, \(t_{P,W}\).
    The protester submit some function of the protocol data \(f(d_{P,W}(\cid, 
      P))\) to the storage \(S\), who learns only that and the time it 
    happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

@@

The players are still the same, but now the adversary controls other players.
In particular, the adversary controls the protester \(P\) and the storage 
\(S\).

\dots

>>>>

This definition is illustrated in \cref{fig:protester-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-protester-adversary.tikz}
  \caption{\label{fig:protester-adversary}%
    An overview of the base protester adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
    and the time it happened, \(t_{P,W}\).
    The protester submit some function of the protocol data \(f(d_{P,W}(\cid, 
      P))\) to the storage \(S\), who learns only that and the time it 
    happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

@@

The players are still the same, but now the adversary controls other players: 
in particular, the adversary controls the protester \(P\) and the storage 
\(S\).

\begin{definition}[Base witness adversary]\label{base-witness-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W)\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(P\) and \(S\).
\end{definition}

\Cref{base-witness-adversary} is the analogous to 
\cref{base-protester-adversary}.
It is illustrated in \cref{fig:witness-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-witness-adversary.tikz}
  \caption{\label{fig:witness-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
    time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{P,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}
